### 2013-09-29 tex/scam/appendix.tex
various updates

\begin{theorem} 
The following holds regardless of whether we impose the boundness and smoothness condition in optimization~\ref{opt:alternate_opt} or not.

@@

Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1})$ be the residue.

@@

\begin{proof}
We will omit the boundness and smoothness constraints in our proof here. It is easy to add those in and check that the result of the theorem still holds.

We will show that with $\hat{d}_k, \hat{c}_k$ as constructed, we can set the dual variables to satisfy complementary slackness and stationary conditions: $\nabla_{d_k, c_k} L(\hat{d})  = 0$ for all $k$.

we can re-write the Lagrangian $L$, in term of just $d_k,c_k$, as the following.
\[
\min_{d_k, c_k}  \frac{1}{2n} \| r_k - \Delta_k d_k + c_k \mathbf{1} \|_2^2 + \lambda \sum_{i=2}^n d_{ki} + \lambda|d_{k1}| - \mu_k^\tran d_k + \gamma_k (c_k - \mathbf{1}^\tran\Delta_k d_k)
\]
where $r_k \coloneqq Y - \sum_{k' \in S, k' \neq k} (\Delta_{k'} d_{k'} - c_{k'} \mathbf{1})$, and $\mu_k \in \R^n$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n$.

@@

\begin{align*}
\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( \hat{r} - \Delta_k \hat{d}_k + \hat{c}_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \hat{r} - \Delta_k d_k + c_k \mathbf{1}) + \gamma_k
\end{align*}
In the derivatives, $\mathbf{u}$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.

>>>>

\begin{theorem} 
The following holds regardless of whether we impose the boundedness and smoothness condition in optimization~\ref{opt:alternate_opt} or not.

@@

Let $\hat{r} \coloneqq Y - \bar{Y} \mathbf{1}_n - \sum_{k \in S} (\Delta_k \hat{d}_k - \hat{c}_k \mathbf{1}_n) $ be the residue.

@@

\begin{proof}
We will omit the boundedness and smoothness constraints in our proof here. It is easy to add those in and check that the result of the theorem still holds.

We will show that with $\hat{d}_k, \hat{c}_k$ as constructed, we can set the dual variables to satisfy complementary slackness and stationary conditions: $\nabla_{d_k, c_k} L(\hat{d})  = 0$ for all $k$.\\

we can re-write the Lagrangian $L$, in term of just $d_k,c_k$, as the following.
\[
\min_{d_k, c_k}  \frac{1}{2n} \| r_k - \Delta_k d_k + c_k \mathbf{1} \|_2^2 
        + \lambda \sum_{i=2}^n d_{ki} + \lambda|d_{k1}| 
        - \mu_k^\tran d_k + \gamma_k (c_k - \mathbf{1}_n^\tran\Delta_k d_k)
\]
where $r_k \coloneqq Y - \bar{Y}\mathbf{1}_n - \sum_{k' \in S, k' \neq k} (\Delta_{k'} d_{k'} - c_{k'} \mathbf{1}_n) $, and $\mu_k \in \R^n$ is a vector of dual variables where $\mu_{k,1} = 0$ and $\mu_{k,i} \geq 0$ for $i=2,...,n$.

@@

\begin{align*}
\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( \hat{r}_k - \Delta_k \hat{d}_k + \hat{c}_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( \hat{r}_k - \Delta_k d_k + c_k \mathbf{1}) + \gamma_k
\end{align*}
In the derivatives, $\mathbf{u}$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.

### 2013-09-29 tex/scam/sparsistency.tex
various updates

\begin{theorem} (Deterministic setting)
\label{thm:deterministic}
Let $\{\hat{d}_k, \hat{c}_k, \hat{\mu} \}_{k \in S}$ be the minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.
Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k -
\hat{c}_k \mathbf{1}) - \hat{\mu}$ be the restricted regression residual. For $k
\in \{1,...,p\}$, $\Delta_{k, j}$, the $j$-th column of $\Delta_k$, is the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$. 
Suppose for all $j$ and all $k\in S^c$, $\lambda_n > | \frac{1}{n}
\hat{r}^\tran \Delta_{k,j}|$. Then $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}. Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\end{theorem}
This result holds regardless of whether we impose the boundness and Lipschitz conditions in optimization~\ref{opt:alternate_opt}.
The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.

@@

\begin{packed_enum}
\item Let $\mathcal{X} = [-b, b]^p$. Let $F$ be a distribution supported and positive on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $F$. 
\item Let $Y = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise. Let $Y^{(1)},...,Y^{(n)}$ be $n$ samples of $Y$.
\item Let $s \leq p$ be a positive integer. Let $S = \{1,...,s\}$ denote the relevant variables, i.e.,
  $f_0(X) = f_0(X_S)$.
\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k) -\mu )^2 \,|\, \E[f_k(X_k)] = 0 \}$ where $\mu = \Ef(X)$.
\end{packed_enum}

>>>>

\begin{theorem} (Deterministic setting)
\label{thm:deterministic}
Let $\{\hat{d}_k, \hat{c}_k\}_{k \in S}$ be the minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.
Let $\hat{r} \coloneqq Y - \bar{Y}\mathbf{1}_n - \sum_{k \in S} (\Delta_k \hat{d}_k -
\hat{c}_k \mathbf{1}_n)$ be the restricted regression residual. For $k
\in \{1,...,p\}$, Let $\Delta_{k, j}$ be the $j$-th column of $\Delta_k$, i.e. the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$. \\

Suppose for all $j$ and all $k\in S^c$, $\lambda_n > | \frac{1}{n}
\hat{r}^\tran \Delta_{k,j}|$. Then $\hat{\mu}$ and $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}. Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\end{theorem}

This result holds regardless of whether we impose the boundedness and Lipschitz conditions in optimization~\ref{opt:alternate_opt}.
The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.

@@

\begin{packed_enum}
\item Let $\mathcal{X} = [-b, b]^p$. Let $F$ be a distribution supported and positive on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be iid samples from $F$.
\item Let $Y = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise. Let $Y^{(1)},...,Y^{(n)}$ be iid samples.
\item Let $s \leq p$ be a positive integer. Let $S = \{1,...,s\}$ denote the relevant variables, i.e.,
  $f_0(X) = f_0(X_S)$.
\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k))^2 \,|\, \E[f_k(X_k)] = 0 \}$ where $\mu = \E f(X)$.
\end{packed_enum}
